---
title: "Multiple Choice Survey Data Clean"
output: html_document
date: '2022-05-04'
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(janitor)
library(readxl)
```

# Qualtrics

When downloading there are two choice:

> Numeric responses or choice text
> 
> - Use numeric values
> 
> - Use choice text

```{r}
qualtrics_raw <- read_excel("data/qualtrics-data.xls") %>% 
  clean_names()
```

The first row of the data provides the question labels used in the original survey. We can make use of this as follows:

```{r}
qualtrics_column_labels <- qualtrics_raw %>% 
  slice(1) %>% 
  pivot_longer(everything(),
               names_to = "column_name",
               values_to = "column_label")
```

Let's remove this and continue with our analysis

```{r}
qualtrics_survey_data <- qualtrics_raw %>% 
  slice(-1) %>% 
  select(start_date, starts_with("q"))
```

We can separate all the observations with separate_rows()

```{r}
qualtrics_long <- qualtrics_survey_data %>% 
  separate_rows(q2, sep = ",")
```

There's an argument for brining the q2_7_text column into q2 but that can make data visualisations harder.

```{r}
qualtrics_long %>% 
  count(q2) %>% 
  mutate(q2 = fct_reorder(q2, n)) %>% 
  ggplot(aes(x = n,
             y = q2)) +
  geom_col()
```

# Survey Monkey

The export format is very messy.

```{r}
survey_monkey_raw <- read_excel("data/survey-monkey-data.xlsx") %>% 
  clean_names()
```

The first row gives us each of the options, which need to be dropped. This format doesn't provide a count for "Other" responses, which we're going to insert as follows and then make long

```{r}
survey_monkey_tidy <- survey_monkey_raw %>% 
  slice(-1) %>% 
  mutate(other_supplied = ifelse(is.na(x8), NA, "Other (WHAT'S YOUR HOBBY?)")) %>% 
  pivot_longer(cols = -c(start_date, x8)) %>% 
  mutate(value = str_remove(value, "- ")) %>% 
  select(start_date, value, x8) %>% 
  filter(!is.na(value))
```


```{r}
survey_monkey_tidy %>% 
  filter(!is.na(value)) %>% 
  count(value) %>% 
  mutate(value = fct_reorder(value, n)) %>% 
  ggplot(aes(x = n,
             y = value)) +
  geom_col()
```

# Google Forms

The Google Forms format is probably the simplest format.

However it has the complexity of not recording the free-form text as an option. Instead all responses are separated with commas. This could issues if the free form text contains commas!

```{r}
google_forms_raw <- read_excel("data/google-forms-data.xlsx") %>% 
  clean_names()
```


```{r}
google_forms_long <- google_forms_raw %>% 
  separate_rows(select_all_the_things_youve_done_in_the_past_24hours,
                sep = ", ")
```

We need to manually specify the explicit options given in the survey:

```{r}
survey_question_options <- c("Slept", "Eaten food", "Cooked food", "Gone to work", "Commuted for work", 
"Relaxed with a hobby (TELL US THE HOBBY BY TYPING IN THE OTHER FIELD)", 
"Other (WHAT'S YOUR HOBBY?)")
```

```{r}
google_forms_tidy <- google_forms_long %>% 
  mutate(response_label = ifelse(select_all_the_things_youve_done_in_the_past_24hours %in% survey_question_options,
                                 select_all_the_things_youve_done_in_the_past_24hours,
                                 "Other (WHAT'S YOUR HOBBY?)"))
```

```{r}
google_forms_tidy %>% 
  filter(!is.na(response_label)) %>% 
  count(response_label) %>% 
  mutate(response_label = fct_reorder(response_label, n)) %>% 
  ggplot(aes(x = n,
             y = response_label)) +
  geom_col()
```












