---
title: "Multiple Choice Survey Data Clean"
output: html_document
date: '2022-05-04'
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(janitor)
library(readxl)
library(writexl)
```

# Qualtrics

When downloading there are two choice:

> Numeric responses or choice text
> 
> - Use numeric values
> 
> - Use choice text

## Original raw data

This survey had 134 responses (more than any other!) so we're going to process this dataset and re-export into the other formats.


```{r}
qualtrics_raw <- read_excel("data-raw/qualtrics_original_choice-text.xlsx") %>% 
  clean_names()
```

The first row of the data provides the question labels used in the original survey. We can make use of this as follows:

```{r}
qualtrics_column_labels <- qualtrics_raw %>% 
  slice(1) %>% 
  pivot_longer(everything(),
               names_to = "column_name",
               values_to = "column_label")
```

Let's remove this and continue with our analysis

```{r}
qualtrics_survey_data <- qualtrics_raw %>% 
  slice(-1) %>% 
  select(start_date, starts_with("q"))
```


We can separate all the observations with separate_rows()

```{r}
qualtrics_long <- qualtrics_survey_data %>% 
  separate_rows(q2, sep = ",")
```

But we need to decide what to do about the write in option. The approach I'd use would be as follows.

```{r}
qualtrics_tidy <- qualtrics_long %>% 
  mutate(q2 = ifelse(q2 == "Other (WHAT'S YOUR HOBBY?)", q2_7_text, q2)) %>% 
  select(-q2_7_text)
```

## Export for Google Drive

```{r}
export_partial_google_forms <- qualtrics_survey_data %>% 
  mutate(q2 = str_replace_all(q2, ",", ", ")) %>% 
  mutate(google_form_format = str_replace(q2, "Other [(]WHAT'S YOUR HOBBY\\?[)]", q2_7_text)) %>% 
  mutate(row_id = row_number()) %>% 
  select(row_id, google_form_format)
```

```{r}
read_excel("data-raw/qualtrics_original_choice-text.xlsx", skip = 1) %>% 
  clean_names() %>% 
  select(start_date) %>% 
  mutate(start_date = as.character(start_date)) %>% 
  bind_cols(export_partial_google_forms) %>% 
  select(start_date, google_form_format) %>% 
  rename("Select all the things you've done in the past 24hours." = google_form_format,
         Timestamp = start_date) %>% 
  write_xlsx("data/google-forms-data.xlsx")
```

## Export for Survey Monkey

```{r}
export_partial_survey_monkey <- qualtrics_long %>% 
  mutate(q2_again = q2) %>% 
  pivot_wider(values_from = q2,
              names_from = q2_again) %>% 
  relocate(q2_7_text, .after = last_col()) %>% 
  clean_names() %>% 
  select(-other_whats_your_hobby, -start_date) %>% 
  mutate(across(slept:relaxed_with_a_hobby_tell_us_the_hobby_by_typing_in_the_other_field, ~paste0("- ", .x)),
         across(slept:relaxed_with_a_hobby_tell_us_the_hobby_by_typing_in_the_other_field, ~na_if(.x, "- NA"))) %>% 
  mutate(across(everything(), ~replace_na(.x, "")))
```

```{r}
read_excel("data-raw/qualtrics_original_choice-text.xlsx", skip = 1) %>% 
  clean_names() %>% 
  select(start_date) %>% 
  mutate(start_date = as.character(start_date)) %>% 
  bind_cols(export_partial_survey_monkey) %>% 
  write_xlsx("data-raw/survey-monkey_exported.xlsx")
```









